Neighbourhood

### 2025-01-17 docsrc/documentation/notebooks/household_income.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

---
title: "Household Income"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # useful for debugging.
---

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

@@

```{r, hh_income_data}
continuous_density("hh_income")  
```

@@

```{r income_output, echo=FALSE}
options(width=120)
ols_output("../../../data/transitions/test/hh_income_2018_2019.rds")
ols_histogram("../../../data/transitions/test/hh_income_2018_2019.rds", "hh_income_next")  
```

>>>>

---
title: "Household Income"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`" # finally figure out how to combine these for debugging and actual 
---

```{r load_data, include=FALSE}
library(here)
source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "hh_income", "glmm", "hh_income_new_GLMM.rds")
model <- readRDS(model_path)

obs <- model@frame$hh_income
preds <- predict(model, type='response')
v <- "hh_income"
```

@@

```{r, hh_income_data}
continuous_density(obs)  
```

@@

```{r income_output, echo=FALSE}
options(width=120)
continuous_densities(obs, preds, v)
print(summary(model))
plot(model)
```

### 2025-01-17 docsrc/documentation/notebooks/neighbourhood.Rmd

---
title: "Neighbourhood"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

@@

```{r neighbourhood_setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

@@

```{r neighbourhood_barchart, echo=FALSE}
print(table(real_data$neighbourhood_safety))
discrete_barplot("neighbourhood_safety")
getwd()
```

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds", "neighbourhood_safety_next")
clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds")
```

>>>>

---
title: "Neighbourhood"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"

---

```{r setup, include=FALSE}
library(here)
library(glmnet)
library(plyr)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "neighbourhood_safety", "rfo", "neighbourhood_safety_RFO.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$neighbourhood_safety
data$neighbourhood_safety_last <- data$neighbourhood_safety

preds <- ranger::predictions(stats::predict(model, data))
column_names <- colnames(preds)
preds <-glmnet::rmult(preds)
preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
v <- " neighbourhood_safety"

```

@@

@@

```{r neighbourhood_barchart, echo=FALSE}
discrete_barplot(obs, 'neighbourhood_safety')
```

@@

```{r housing_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, "neighbourhood_safety") 
rfo_output(model)
```
